---
title: "Help Seeking Behavior in Austrian General Population"
author: "Marina Zeldovich"
date: "2024-12-09"
output: html_document
toc: true
---

# Packages {.tabset .tabset-fade .tabset-pills}

```{r packages, message=FALSE, warning=FALSE}
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(table1)
library(likert)
library(psych)
library(viridis)
library(corrplot)
library(lavaan)
library(semPlot)
library(emmeans)
library(car)
```

# Data {.tabset .tabset-fade .tabset-pills}

```{r data}
load("data_cleaned.RData")
```

```{r data overview}
# glimpse(d1)
```

# Descriptive Statistics {.tabset .tabset-fade .tabset-pills}

```{r descriptive}
#sociodemographics
table1(~gender +
       age +
       education +
       income +
       occupation +
       state +
       migration +
       german_mother_tongue +
       marital,
       digits.pct = 0,
#       round.median.min.max = TRUE,
       data = d1)
``` 

```{r}
# symptom burden
table1(~ ghsq_total +
       ghsq_fam_friends +
       ghsq_professionals +
       ghsq_semiprofessionals +
       ssosh_total +
       soep_total +
       soep_total_cat +
       pss_total +
       pss_total_cat +
       phq_total +
       phq_total_cat_dicho +
       gad_total +
       gad_total_cat_dicho, data = d1)
```

```{r}
quantile(d1$soep_total, probs = 0.80)
```

# GHSQ {.tabset .tabset-fade .tabset-pills}

## Reliability

```{r ghsq-reliability1}
psych::reliability(d1 %>% dplyr::select("ghsq1":"ghsq10"))  # alpha = 0.71, omega = 0.75
```

The subscale realiability is rather low.

```{r ghsq-reliability fam friends}
# psych::reliability(d1 %>% dplyr::select("ghsq1":"ghsq4"))  # alpha = 0.64, omega = 0.70
```

```{r ghsq-reliability professionals}
# psych::reliability(d1 %>% dplyr::select("ghsq5", "ghsq7", "ghsq9")) # alpha = 0.57, omega = 0.62
```

```{r ghsq-reliability semiprofessionals}
# psych::reliability(d1 %>% dplyr::select("ghsq6", "ghsq8")) # no estimates
```

## Response patterns

```{r ghsq-patterns}
table1(~ as.factor(ghsq1) +
         as.factor(ghsq2) +
         as.factor(ghsq3) +
         as.factor(ghsq4) +
         as.factor(ghsq5) +
         as.factor(ghsq6) +
         as.factor(ghsq7) +
         as.factor(ghsq8) +
         as.factor(ghsq9) +
         as.factor(ghsq10),
       data = d1)
```

```{r}
ghsq_items <- c("Intimate partner",
                "Friend",
                "Parent",
                "Other relative",
                "Mental health professional",
                "Help line",
                "General practitioner",
                "Minister or religious leader",
                "Other",
                "None")

ghsq_values <- c("Extremely unlikely", "2", "Unlikely", "4", "Likely", "6", "Extremely likely")
```

```{r}
ghsq_pct <-
  d1 %>%
  dplyr::select(ghsq1:ghsq10) %>%  
  setNames(ghsq_items) %>%              # Rename the columns using item short names
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>%
  mutate(value = factor(value, levels = 1:7, labels = ghsq_values)) %>%  # Transform values to factors
  group_by(variable, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(variable) %>%                 # Group by variable for percentage calculation
  mutate(percentage = (count / sum(count)) * 100) %>%  # Calculate percentages
  select(-count) %>%                     # Remove count column
  pivot_wider(names_from = variable, values_from = percentage, values_fill = 0) %>% # Final table
  select(value, all_of(ghsq_items))  # Ensure column order matches GHSQ item appereance in the questionnaire
```

```{r fig.width=10, fig.height=5}
#pdf("02_figures/Figure2_Helpseeking.pdf", width = 10, height = 5)
ghsq_pct %>%
  pivot_longer(cols = -value, names_to = "variable", values_to = "percentage") %>%
  mutate(variable = factor(variable, levels = rev(ghsq_items))) %>% 
  ggplot(aes(x = variable, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(percentage > 5, sprintf("%.1f%%", percentage), ""),
                color = value), 
            size = 3,
            position = position_stack(vjust = 0.5)) +
  coord_flip() +  # Flip the axes
  scale_fill_viridis_d() +  # Apply viridis color palette
  scale_color_manual(values = c("Extremely unlikely" = "white",
                                "2" = "white",
                                "Unlikely" = "white",
                                "4" = "white",
                                "Likely" = "black",
                                "6" = "black",
                                "Extremely likely" = "black")) + 
  theme_minimal() +
   guides(fill = guide_legend(nrow = 1, 
                              override.aes = list(label = ""),
                              reverse = T), 
          color = guide_legend(nrow = 1, 
                               reverse = T)) + # Display color legend in one line
  labs(x = "", 
       y = "Percentage", fill = "", color = "") +  # Add legend for color, skip letters, reverse order
  theme(axis.text.y = element_text(size = 10), 
        legend.text = element_text(size = 10), 
        legend.position = "bottom")
#dev.off()
```

## Help received

```{r}
# at least one clinically relevant stress or symptom burden

d1$burden <- 
  ifelse(d1$soep_total_cat == "notable level of loneliness" |
           d1$isi_total_cat_dicho == "clinical insomnia" |
           d1$cage_total_cat == "suspected alcohol misuse" |
           d1$pss_total_cat == "high stress" | 
           d1$phq_total_cat_dicho == "clinical level of depression" | 
           d1$gad_total_cat_dicho == "clinical level of anxiety", 1, 0)

```

```{r}
d1$burden <- factor(d1$burden, levels = 0:1, labels = c("No burden", "Stress/symptom burden"))
```

```{r}
prop.table(table(d1$burden))
```

```{r}
# ghsq_received <- d1 %>%
#   dplyr::select(gender, age, migration, state, ghsq_help1:ghsq_help8, ghsq_help10)
```

```{r}
# ghsq_received[grepl("ghsq", names(ghsq_received))] <- 
#   apply(ghsq_received[grepl("ghsq", names(ghsq_received))], 2, function(x){ifelse(x == 1, 0, 1)})
```

```{r}
ghsq_received_items <- c("Intimate \n partner",
                "Friend",
                "Parent",
                "Other \n relative",
                "Mental health \n professional",
                "Help line",
                "General \n practitioner",
                "Minister or \n religious leader",
                "Other",
                "None")
```


```{r}
ghsq_received_values <- c("Yes", "No")
```

```{r}
ghsq_received_pct <-
  d1 %>%
  dplyr::select(ghsq_help1:ghsq_help10) %>%  
  setNames(ghsq_received_items) %>%             
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>%
  mutate(value = factor(value, levels = 1:2, labels = ghsq_received_values)) %>%  
  group_by(variable, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(variable) %>%                 
  mutate(percentage = (count / sum(count)) * 100) %>%  
  select(-count) %>%                     
  pivot_wider(names_from = variable, values_from = percentage, values_fill = 0) %>% 
  select(value, all_of(ghsq_received_items))
```

```{r fig.width=10, fig.height=5}
#pdf("02_figures/FigureA2_Helpreceived.pdf", width = 10, height = 5)
ghsq_received_pct %>% 
  pivot_longer(cols = -value, names_to = "variable", values_to = "percentage") %>%
  mutate(variable = factor(variable, levels = ghsq_received_items)) %>% 
  ggplot(aes(x = variable, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(percentage > 5, sprintf("%.1f%%", percentage), ""),
                color = value), 
            size = 3,
            position = position_stack(vjust = 0.5)) +
  scale_fill_viridis_d() +  
  scale_color_manual(values = c("No" = "black",
                                "Yes" = "white")) + 
  theme_minimal() +
  guides(fill = guide_legend(nrow = 1, 
                             override.aes = list(label = ""),
                             reverse = F), 
         color = guide_legend(nrow = 1, 
                              reverse = F)) + 
  labs(x = "", 
       y = "Percentage", fill = "", color = "") +  
  theme(axis.text.y = element_text(size = 10), 
        legend.text = element_text(size = 10), 
        legend.position = "bottom")
#dev.off()
```

```{r}
ghsq_received_pct2 <-
  d1 %>%
  dplyr::select(burden, ghsq_help1:ghsq_help10) %>%  
  setNames(c("burden", ghsq_received_items)) %>%               
  pivot_longer(cols = -burden, names_to = "variable", values_to = "value") %>%
  mutate(value = factor(value, levels = 1:2, labels = ghsq_received_values)) %>%  
  group_by(burden, variable, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(burden, variable) %>%  
  mutate(percentage = (count / sum(count)) * 100) %>%  
  select(-count) %>%  # Remove count column
  pivot_wider(names_from = variable, values_from = percentage, values_fill = 0) %>% 
  select(burden, value, all_of(ghsq_received_items))

```

```{r fig.width=10, fig.height=7}
#pdf("02_figures/Figure3_Helpreceived.pdf", width = 10, height = 5)
# Plot grouped by burden
ghsq_received_pct2 %>% 
  pivot_longer(cols = -c(burden, value), names_to = "variable", values_to = "percentage") %>%
  mutate(variable = factor(variable, levels = ghsq_received_items)) %>%
  ggplot(aes(x = variable, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(percentage > 5, sprintf("%.1f%%", percentage), ""),
                color = value),
            size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_viridis_d() +  
  scale_color_manual(values = c("No" = "black",
                                "Yes" = "white")) + 
  theme_minimal() +
  guides(fill = guide_legend(nrow = 1, 
                             override.aes = list(label = ""),
                             reverse = F), 
         color = guide_legend(nrow = 1, 
                              reverse = F)) +
  labs(x = "", 
       y = "Percentage", fill = "", color = "") +
  theme(axis.text.y = element_text(size = 10), 
        legend.text = element_text(size = 10), 
        legend.position = "bottom") +
  facet_wrap(~burden, ncol = 1)  
#dev.off()
```

# Self-stigmatization {.tabset .tabset-fade .tabset-pills}

## Reliability

```{r self-stigmatization-reliability}
psych::reliability(d1 %>% dplyr::select("ssosh1":"ssosh10"))
```
# Symptom burden {.tabset .tabset-fade .tabset-pills}

## Correlation matrix

```{r}
cor_data <-
  d1 %>%
  dplyr::select(ghsq_total, ghsq_fam_friends, ghsq_professionals, ghsq_semiprofessionals, 
                ssosh_total, soep_total, isi_total, cage_total, pss_total, phq_total, gad_total)
```

```{r}
cor_matrix <- cor(cor_data %>% dplyr::select(ghsq_total, ghsq_fam_friends, ghsq_professionals, ghsq_semiprofessionals,
                                       ssosh_total, soep_total, isi_total, cage_total, pss_total, phq_total, gad_total))
```

```{r}
cor_labels <- c("GHSQ Total", "GHSQ Family and Friends", "GHSQ Professionals", "GHSQ Semiprofessionals", 
                "SSOSH", "SOEP", "ISI-7", "CAGE", "PSS-4", "PHQ-9", "GAD-7")

```

```{r}
rownames(cor_matrix) <- cor_labels
colnames(cor_matrix) <- cor_labels
```

```{r fig.width=6, fig.height=6}
#pdf("02_figures/Figure4_Correlations.pdf", width = 8, height = 7)
corrplot(cor_matrix, 
         method = "number", 
         type = "upper", 
         tl.col = "black", 
         tl.cex = 0.8,
         col = viridis(100),
         diag = FALSE)
#dev.off()
```

# Moderator analysis {.tabset .tabset-fade .tabset-pills}

Moderator analysis while controlling for age, gender, state and migration back ground. State is defined as Vienna vs. rest, diverse participants dropped due low number of cases ($n = 4$).

```{r}
d1$state_dicho <- ifelse(d1$state == "Vienna", 1, 0)
```

```{r}
d1$state_dicho <- factor(d1$state_dicho, levels = c(0, 1), labels = c("Rest of Austria", "Vienna"))
```

```{r}
d2 <- d1 %>% dplyr::select(., 
             age,
             gender,
             state_dicho,
             migration,
             ghsq_total,
             ssosh_total,
             soep_total,
             isi_total,
             cage_total,
             pss_total,
             phq_total,
             gad_total) %>%
  filter(., gender != "diverse") # N = 2021
```

## Loneliness

### Model

```{r}
res1 <- lm(ghsq_total ~ age + gender + state_dicho + migration + soep_total * ssosh_total, data = d2) 
```

```{r}
summary(res1)
```

### CI

```{r}
cbind(coef(res1), confint(res1, level = 0.95))
```
### Residuals

```{r fig.width=4, fig.height=4}
plot(res1$fitted, res1$residuals)
```

### Estimated marginal means

```{r}
# same moderator for all analyses
m_ssosh_total <- round(mean(d2$ssosh_total, na.rm = TRUE), 2)
sd_ssosh_total <- round(sd(d2$ssosh_total, na.rm = TRUE), 2)
```

```{r}
# varying outcomes
m_soep_total <- round(mean(d2$soep_total, na.rm = TRUE), 2)
sd_soep_total <- round(sd(d2$soep_total, na.rm = TRUE), 2)
```

Differences in different levels of Loneliness.

```{r}
emm_res1 <- emmeans(res1,  ~ soep_total*ssosh_total,
  cov.keep = 3, at = list(
  soep_total = c(round(m_soep_total - sd_soep_total, 2), 
                 m_soep_total, 
                 round(m_soep_total + sd_soep_total, 2)),
  ssosh = c(round(m_ssosh_total - sd_ssosh_total, 2), 
            m_ssosh_total, 
            round(m_ssosh_total + sd_ssosh_total,2))), level = 0.95)
```

```{r}
summary(emm_res1)
```

### Simple slopes

```{r}
simpleSlope_res1 <- emtrends(res1, pairwise ~ ssosh_total, var = "soep_total", cov.keep = 3, 
                        at = list(ssosh_total = c(round(m_ssosh_total - sd_ssosh_total, 2), 
                                            m_ssosh_total, 
                                            round(m_ssosh_total + sd_ssosh_total, 2))), level = 0.95)
```

```{r}
summary(simpleSlope_res1)
```
### Visualization

```{r}
plot_res1 <- emmip(res1, ssosh_total ~ soep_total,
  cov.keep = 3, at = list(
    soep_total = c(m_soep_total - sd_soep_total, m_soep_total, m_soep_total + sd_soep_total),
    ssosh_total = c(m_ssosh_total - sd_ssosh_total, 
                    m_ssosh_total, 
                    m_ssosh_total + sd_ssosh_total)),
  xlab = "SOEP (Loneliness)",
  ylab = "GHSQ (Help Seeking Behavior)",
  CIs = TRUE, level = 0.95, position = "jitter") +
 # ggtitle("(A) SOEP (Loneliness)") +
  theme_minimal() + 
  scale_color_viridis_d(name = "SSOSH (Self-stigma)", option = "D", begin = 0, end = 1, direction = 1) +
  #theme(legend.position = "none", plot.margin = unit(c(1, 1, 4, 1), "lines"))
  theme(legend.position = "bottom", legend.key.size = unit(1.5, "lines"))
```

```{r}
#save
pdf("02_figures/Figure5_Moderation_SOEP.pdf", width = 7, height = 5)
plot_res1
dev.off()
```

## Insomnia

### Model

```{r}
res2 <- lm(ghsq_total ~ age + gender + state_dicho + migration + isi_total * ssosh_total, data = d2) 
```

```{r}
summary(res2)
```

### CI

```{r}
cbind(coef(res2), confint(res2, level = 0.95))
```
### Residuals

```{r fig.width=4, fig.height=4}
plot(res2$fitted, res2$residuals)
```

### Estimated marginal means

```{r}
# varying outcomes
m_isi_total <- round(mean(d2$isi_total, na.rm = TRUE), 2)
sd_isi_total <- round(sd(d2$isi_total, na.rm = TRUE), 2)
```

Differences in different levels of Insomnia.

```{r}
emm_res2 <- emmeans(res2,  ~ isi_total*ssosh_total,
  cov.keep = 3, at = list(
  isi_total = c(round(m_isi_total - sd_isi_total, 2), 
                 m_isi_total, 
                 round(m_isi_total + sd_isi_total, 2)),
  ssosh = c(round(m_ssosh_total - sd_ssosh_total, 2), 
            m_ssosh_total, 
            round(m_ssosh_total + sd_ssosh_total,2))), level = 0.95)
```

```{r}
summary(emm_res2)
```
### Simple slopes

```{r}
simpleSlope_res2 <- emtrends(res2, pairwise ~ ssosh_total, var = "isi_total", cov.keep = 3, 
                        at = list(ssosh_total = c(round(m_ssosh_total - sd_ssosh_total, 2), 
                                            m_ssosh_total, 
                                            round(m_ssosh_total + sd_ssosh_total, 2))), level = 0.95)
```

```{r}
summary(simpleSlope_res2)
```
### Visualization

```{r}
plot_res2 <- emmip(res2, ssosh_total ~ isi_total,
  cov.keep = 3, at = list(
    isi_total = c(m_isi_total - sd_isi_total, m_isi_total, m_isi_total + sd_isi_total),
    ssosh_total = c(m_ssosh_total - sd_ssosh_total, 
                    m_ssosh_total, 
                    m_ssosh_total + sd_ssosh_total)),
  xlab = "ISI-7 (Insomnia)",
  ylab = "GHSQ (Help Seeking Behavior)",
  CIs = TRUE, level = 0.95, position = "jitter") +
  ggtitle("(B) ISI-7 (Insomnia)") +
  theme_minimal() + 
  scale_color_viridis_d(name = "SSOSH (Self-stigma)", option = "D", begin = 0, end = 1, direction = 1) +
  theme(legend.position = "none", plot.margin = unit(c(1, 1, 4, 1), "lines"))
```

## Alcohol misuse

### Model

```{r}
res3 <- lm(ghsq_total ~age + gender + state_dicho + migration + cage_total * ssosh_total, data = d2) 
```

```{r}
summary(res3)
```

### CI

```{r}
cbind(coef(res3), confint(res3, level = 0.95))
```

## Stress

### Model

```{r}
res4 <- lm(ghsq_total ~ age + gender + state_dicho + migration + pss_total * ssosh_total, data = d2) 
```

```{r}
summary(res4)
```

### CI

```{r}
cbind(coef(res4), confint(res4, level = 0.95))
```

### Residuals

```{r fig.width=4, fig.height=4}
plot(res4$fitted, res4$residuals)
```

### Estimated marginal means

```{r}
# varying outcomes
m_pss_total <- round(mean(d2$pss_total, na.rm = TRUE), 2)
sd_pss_total <- round(sd(d2$pss_total, na.rm = TRUE), 2)
```

Differences in different levels of Stress.

```{r}
emm_res4 <- emmeans(res4,  ~ pss_total*ssosh_total,
  cov.keep = 3, at = list(
  pss_total = c(round(m_pss_total - sd_pss_total, 2), 
                 m_pss_total, 
                 round(m_pss_total + sd_pss_total, 2)),
  ssosh = c(round(m_ssosh_total - sd_ssosh_total, 2), 
            m_ssosh_total, 
            round(m_ssosh_total + sd_ssosh_total,2))), level = 0.95)
```

```{r}
summary(emm_res4)
```
### Simple slopes

```{r}
simpleSlope_res4 <- emtrends(res4, pairwise ~ ssosh_total, var = "pss_total", cov.keep = 3, 
                        at = list(ssosh_total = c(round(m_ssosh_total - sd_ssosh_total, 2), 
                                            m_ssosh_total, 
                                            round(m_ssosh_total + sd_ssosh_total, 2))), level = 0.95)
```

```{r}
summary(simpleSlope_res4)
```

### Visualization

```{r}
plot_res4 <- emmip(res4, ssosh_total ~ pss_total,
  cov.keep = 3, at = list(
    pss_total = c(m_pss_total - sd_pss_total, m_pss_total, m_pss_total + sd_pss_total),
    ssosh_total = c(m_ssosh_total - sd_ssosh_total, 
                    m_ssosh_total, 
                    m_ssosh_total + sd_ssosh_total)),
  xlab = "PSS-4 (Stress)",
  ylab = "GHSQ (Help Seeking Behavior)",
  CIs = TRUE, level = 0.95, position = "jitter") +
  ggtitle("(B) PSS-4 (Stress)") +
  theme_minimal() + 
  scale_color_viridis_d(name = "SSOSH (Self-stigma)", option = "D", begin = 0, end = 1, direction = 1) +
  theme(legend.position = "none", plot.margin = unit(c(1, 1, 4, 1), "lines"))
```

## Depression

### Model

```{r}
res5 <- lm(ghsq_total ~ age + gender + state_dicho + migration + phq_total * ssosh_total, data = d2) 
```

```{r}
summary(res5)
```

### CI

```{r}
cbind(coef(res5), confint(res5, level = 0.95))
```
### Residuals

```{r fig.width=4, fig.height=4}
plot(res5$fitted, res5$residuals)
```

### Estimated marginal means

```{r}
# varying outcomes
m_phq_total <- round(mean(d2$phq_total, na.rm = TRUE), 2)
sd_phq_total <- round(sd(d2$phq_total, na.rm = TRUE), 2)
```

Differences in different levels of Depression.

```{r}
emm_res5 <- emmeans(res5,  ~ phq_total*ssosh_total,
  cov.keep = 3, at = list(
  phq_total = c(round(m_phq_total - sd_phq_total, 2), 
                 m_phq_total, 
                 round(m_phq_total + sd_phq_total, 2)),
  ssosh = c(round(m_ssosh_total - sd_ssosh_total, 2), 
            m_ssosh_total, 
            round(m_ssosh_total + sd_ssosh_total,2))), level = 0.95)
```

```{r}
summary(emm_res5)
```
### Simple slopes

```{r}
simpleSlope_res5 <- emtrends(res5, pairwise ~ ssosh_total, var = "phq_total", cov.keep = 3, 
                        at = list(ssosh_total = c(round(m_ssosh_total - sd_ssosh_total, 2), 
                                            m_ssosh_total, 
                                            round(m_ssosh_total + sd_ssosh_total, 2))), level = 0.95)
```

```{r}
summary(simpleSlope_res5)
```

### Visualization

```{r}
plot_res5 <- emmip(res5, ssosh_total ~ phq_total,
  cov.keep = 3, at = list(
    phq_total = c(m_phq_total - sd_phq_total, m_phq_total, m_phq_total + sd_phq_total),
    ssosh_total = c(m_ssosh_total - sd_ssosh_total, 
                    m_ssosh_total, 
                    m_ssosh_total + sd_ssosh_total)),
  xlab = "PHQ-9 (Depression)",
  ylab = "GHSQ (Help Seeking Behavior)",
  CIs = TRUE, level = 0.95, position = "jitter") +
  ggtitle("(C) PHQ-9 (Depression)") +
  theme_minimal() + 
  scale_color_viridis_d(name = "SSOSH (Self-stigma)", option = "D", begin = 0, end = 1, direction = 1) +
  theme(legend.position = "none", plot.margin = unit(c(1, 1, 4, 1), "lines"))
```

## Anxiety

### Model

```{r}
res6 <- lm(ghsq_total ~ age + gender + state_dicho + migration + gad_total * ssosh_total, data = d2) 
```

```{r}
summary(res6)
```

### CI

```{r}
cbind(coef(res6), confint(res6, level = 0.95))
```

### Residuals

```{r fig.width=4, fig.height=4}
plot(res6$fitted, res6$residuals)
```

### Estimated marginal means

```{r}
# varying outcomes
m_gad_total <- round(mean(d2$gad_total, na.rm = TRUE), 2)
sd_gad_total <- round(sd(d2$gad_total, na.rm = TRUE), 2)
```

Differences in different levels of Anxiety.

```{r}
emm_res6 <- emmeans(res6,  ~ gad_total*ssosh_total,
  cov.keep = 3, at = list(
  gad_total = c(round(m_gad_total - sd_gad_total, 2), 
                 m_gad_total, 
                 round(m_gad_total + sd_gad_total, 2)),
  ssosh = c(round(m_ssosh_total - sd_ssosh_total, 2), 
            m_ssosh_total, 
            round(m_ssosh_total + sd_ssosh_total,2))), level = 0.95)
```

```{r}
summary(emm_res6)
```
### Simple slopes

```{r}
SimpleSlope_res6 <- emtrends(res6, pairwise ~ ssosh_total, var = "gad_total", cov.keep = 3, 
                        at = list(ssosh_total = c(round(m_ssosh_total - sd_ssosh_total, 2), 
                                            m_ssosh_total, 
                                            round(m_ssosh_total + sd_ssosh_total, 2))), level = 0.95)
```

```{r}
summary(SimpleSlope_res6)
```
### Visualization

```{r}
plot_res6 <- emmip(res6, ssosh_total ~ gad_total,
  cov.keep = 3, at = list(
    gad_total = c(m_gad_total - sd_gad_total, m_gad_total, m_gad_total + sd_gad_total),
    ssosh_total = c(m_ssosh_total - sd_ssosh_total, 
                    m_ssosh_total, 
                    m_ssosh_total + sd_ssosh_total)),
  xlab = "GAD-7 (Anxiety)",
  ylab = "GHSQ (Help Seeking Behavior)",
  CIs = TRUE, level = 0.95, position = "jitter") +
  ggtitle("(D) GAD-7 (Anxiety)") +
  theme_minimal() + 
  scale_color_viridis_d(name = "SSOSH (Self-stigma)", option = "D", begin = 0, end = 1, direction = 1) +
  theme(legend.position = "bottom", legend.key.size = unit(1.5, "lines"))
```


```{r fig.width=10, fig.height=10}
# combine plots

#pdf("02_figures/Figure5_Moderation.pdf", width = 10, height = 10)
#gridExtra::grid.arrange(plot_res1, plot_res2, plot_res3, plot_res4, plot_res5, plot_res6,
#                        ncol = 3)
#dev.off()
```
























